\plaintitle

### 2016-09-21 drafts/labor/relationships.tex
differences

\begin{comment}
\end{comment}

\topic{The differences between crowd workers and pieceworkers seem defined largely by
the differences in the places of work.}
Whereas it arguably became inevitable that workers would have a place to
meet, discuss, and collaborate
when they began sharing places of work,
online spaces make it much harder to do so.
Crowd workers can ``lurk'' and do tasks, or just do the occasional one--off task,
without any affiliation with
--- or even knowledge of ---
communities of peers
% \ali{multiple citations that labor unions came out of factories here}
\cite{miller2011understanding,mcinnis2016one,earl2011digitally}.

\topic{We further find the sources of differences between crowd work and piecework
in the nature of the relationship between workers and requesters
--- or rather, the lack thereof.}
While historically the management of workers had to be done through a foreman
(who necessarily had an intuitive
--- perhaps sympathetic ---
relationship with workers),
the foreman of the \nth{20} century has largely been replaced
by algorithms of the \nth{21} century
\cite{uberAlgorithm}.
The result of this change is that the agents managing work are now
cold and logical, if unforgiving.
Where a person might recognize that the ``attention check'' questions 
proposed by \citeauthor{le2010ensuring} ensure that malicious and inattentive are stopped,
some implementations of these approaches
only seem to antagonize workers \ali{shots fired}
\cite{le2010ensuring,MaliciousCrowdworkersGadiraju}.
% We've known for decades that workers prefer human management 
\citeauthor{10.2307/2555446} told us more than 30 years ago
--- in \citeyear{10.2307/2555446} --- that
``\dots~when performance is difficult to evaluate,
imperfect input measures and
a manager's subjective judgment are preferable to
defective (simple, observable) output measures''
\cite{10.2307/2555446}.
\ali{here's an idea. feel free to push back or revise or something:\\
``Should we be surprised that
management approaches we've known to
frustrate pieceworkers since \citeyear{10.2307/2555446}
would only aggravate crowd workers in many of the same ways?''}

>>>>

\begin{comment}
	*workers make little money but love autonomy --- workers make little money
	workers blamed for quality --- ???
	both cases, sociality is hard
	*collective action hard --- collective action succeeded

	- algorithms, not managers
\end{comment}

While historical pieceworkers could be looked down on, as the match-stick girls were characterized by ``brashness, irregularity, low morality, and little education'', there was generally less written about quality concerns for historical pieceworkers than there is in modern crowd work. 
Why the difference? 
One possibility is that, through writing web scripts and applying them to many tasks, it is possible for a small number of spammers have an outsized influence.
Historically, it was much harder for such workers to move and get new jobs --- today, they can simply accept a different task on Mechanical Turk.
Another possibility: online anonymity breeds distrust~\cite{friedman2000trust}, and where pieceworkers could be directly observed by foremen, online workers are known by little more than an account ID.

% \topic{The differences between crowd workers and pieceworkers seem defined largely by
% the differences in the places of work.}
% Whereas it arguably became inevitable that workers would have a place to
% meet, discuss, and collaborate
% when they began sharing places of work,
% online spaces make it much harder to do so.
% Crowd workers can ``lurk'' and do tasks, or just do the occasional one--off task,
% without any affiliation with
% --- or even knowledge of ---
% communities of peers
% % \ali{multiple citations that labor unions came out of factories here}
% \cite{miller2011understanding,mcinnis2016one,earl2011digitally}.

\topic{The relationship between workers and employers has also shifted: while historically the management of workers had to be done through a foreman
(who necessarily had an intuitive
--- perhaps sympathetic ---
relationship with workers),
the foreman of the \nth{20} century has largely been replaced
by algorithms of the \nth{21} century
\cite{uberAlgorithm}.}
The result of this change is that the agents managing work are now
cold, logical, and unforgiving.
Where a person might recognize that the ``attention check'' questions 
proposed by \citeauthor{le2010ensuring} ensure that malicious and inattentive workers are stopped,
some implementations of these approaches
only seem to antagonize workers.
More than 30 years ago, \citeauthor{10.2307/2555446} wrote:
``When performance is difficult to evaluate,
imperfect input measures and
a manager's subjective judgment are preferable to
defective (simple, observable) output measures''
\cite{10.2307/2555446}.
This frustration has only grown as requesters have had to rely on automatic management mechanisms. Only a few use the equivalent of human foremen~\cite{haas2015argonaut,kulkarni2012mobileworks}.

% \ali{here's an idea. feel free to push back or revise or something:\\
% ``Should we be surprised that
% management approaches we've known to
% frustrate pieceworkers since \citeyear{10.2307/2555446}
% would only aggravate crowd workers in many of the same ways?''}

Relative to the mature state of collective action for pieceworkers offline, crowd workers have struggled to make their voices heard~\cite{dynamo,storiesIraniSilberman,turkopticon}.
Both pieceworkers and crowd workers have struggled at times to form a collective identity necessary to organize.
With workers joining and leaving the crowd labor force continuously, and with many part-time members, it is extremely difficult to corral the group to make a collective decision~\cite{dynamo}.
However, even when they can: whereas pieceworkers could physically block access to a site of production, online labor markets provide no facilities for workers to change the experience of other workers.
This is a key limitation --- without it, workers cannot enforce a strike.
